Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-16 paper.tex

To estimate the uncertainty on fuel cycle output metrics, a Total Monte
Carlo approach has been applied.  In the following, output metric uncertainty
corresponds to the standard deviation of the output metrics over about 200
different simulations.  For each deployed facility, the
parameters are normally distributed with an artificially large standard
deviation of $10\%$.

@@

\subsection{The Fuel Cycle}
This work aims to assess the impact of the operational uncertainties of a simple
transition, inspired from the EG23 fuel cycle
of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}. As shown in Figure \ref{fig:cycle}, this is a
transition from a light water reactor fleet loaded with \gls{UOX} fuel to a
sodium fast reactor fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
of the generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with each operational parameter associated with an
  uncertainty labeled in green.}\label{fig:cycle}
\end{figure}

@@

>>>>

To estimate the uncertainty on fuel cycle output metrics, a Total Monte
Carlo approach has been applied.  In the following, output metric uncertainty
corresponds to the standard deviation of the output metrics 199
different simulations.  For each deployed facility, the
parameters are normally distributed with an artificially large standard
deviation of $10\%$.

@@

\subsection{The Fuel Cycle Scenario}
This work aims to assess the impact of the operational uncertainties of a simple
transition, inspired from the EG23 fuel cycle
of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}. As shown in Figure \ref{fig:cycle}, this is a
transition from a light water reactor fleet loaded with \gls{UOX} fuel to a
sodium fast reactor fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
of the generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with each operational parameter associated with an
  uncertainty labeled in green.}\label{fig:cycle}
\end{figure}

@@

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{Leniau2015125} which
calculates the fissile fraction required in the fuel to reach a target
burnup at the end of irradiation.  In this study, the uncertainty on the fuel
enrichment is not applied directly on the effective enrichment but on the target
parameter (the burnup), which leads to a fuel enrichment uncertainty close to
$10\%$.
